% Main Manuscript File - EES Submission
% Quantum Spectral Engineering for Enhanced Agrivoltaic Efficiency

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts,graphicx,booktabs,bm,multirow,siunitx,physics}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{natbib}
\usepackage[margin=2.cm]{geometry}

% Hyperref setup
\hypersetup{
    pdftitle={Quantum Spectral Engineering for Enhanced Agrivoltaic Efficiency - Main Manuscript},
    pdfauthor={Teguia et al.},
    pdfsubject={Quantum Photosynthesis, Agrivoltaics, Non-Markovian Dynamics},
    pdfkeywords={agrivoltaics, quantum photosynthesis, spectral engineering, non-Markovian dynamics, renewable energy},
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\DeclareSIUnit{\yr}{yr}
\DeclareSIUnit{\tonne}{t}
\DeclareSIUnit{\hectare}{ha}
\DeclareSIUnit{\kWh}{kWh}

%=============================================================================
% TITLE AND AUTHORS
%=============================================================================

\title{\textbf{Quantum Spectral Engineering for Enhanced Agrivoltaic Efficiency: Non-Markovian Dynamics in Photosynthetic Energy Transfer}}

\author{
    Steve Cabrel Teguia Kouam$^{2,*}$,
    Theodore Goumai Vedekoi$^{1}$, 
    Jean-Pierre Tchapet Njafa$^{1}$, \\
    Jean-Pierre Nguenang$^{2}$,
    Serge Guy Nana Engo$^{1}$ \\
    \\
    $^{1}$Department of Physics, Faculty of Science, University of Yaoundé I, Cameroon \\
    $^{2}$Department of Physics, Faculty of Science, University of Douala, Cameroon \\
    \\
    $^{*}$Corresponding author: \texttt{steve.teguia@univ-douala.cm}
}

\date{\today}

%=============================================================================
% DOCUMENT BEGIN
%=============================================================================

\begin{document}

\maketitle

%=============================================================================
% ABSTRACT
%=============================================================================

\begin{abstract}
Agrivoltaic systems integrate crop production with solar energy generation, but current designs treat light as a classical photon flux without considering the quantum nature of photosynthetic energy transfer. Here, we introduce spectral bath engineering---strategic spectral filtering through semi-transparent organic photovoltaic (OPV) panels to exploit non-Markovian quantum coherence in photosynthesis. Using adaptive Hierarchy of Pure States (adHOPS) simulations of the Fenna-Matthews-Olsen complex, we show that selective filtering at vibronic resonance wavelengths (\SIlist{750;820}{\nano\meter} dual-band) improves the electron transport rate (ETR) by \SI{25}{\percent} relative to Markovian models under matched photon flux. Coherence lifetimes increase by \SIrange{20}{50}{\percent}, pairwise concurrence nearly doubles (\SI{+89}{\percent}), and exciton delocalization extends from \numrange{3}{5} to \numrange{8}{10} chromophores. A 12-test validation suite confirms robustness at physiological temperature (\SI{295}{\kelvin}) and under realistic static disorder ($\sigma = \SI{50}{\per\cm}$). Geographic simulations across nine climate zones---including five sub-Saharan African sites---show persistent quantum advantages of \SIrange{18}{26}{\percent}. Pareto optimization identifies balanced configurations achieving \SIrange{16}{18}{\percent} power conversion efficiency with \SIrange{15}{20}{\percent} ETR enhancement, yielding an estimated USD~\numrange{470}{3000}\,\si{ha^{-1}\,yr^{-1}} additional revenue. We provide materials specifications and testable predictions for ultrafast spectroscopy and field trials.
\end{abstract}

%=============================================================================
% BROADER CONTEXT
%=============================================================================

\noindent\textbf{Broader context}

Meeting rising global demand for both food and clean energy requires new approaches to land-use optimization. Agrivoltaic systems---co-locating solar panels with crop production---offer a promising solution, yet existing designs rely on classical optics that ignore how plants actually use light at the molecular level. In photosynthetic pigment-protein complexes, energy transfer is governed by quantum mechanical processes sensitive to the spectral composition of incident light. This work shows that by engineering the transmission spectrum of semi-transparent solar panels to target specific vibronic resonances in photosynthetic systems, it is possible to enhance biological energy transfer efficiency while simultaneously generating electricity. The approach bridges quantum biology and renewable energy engineering, providing quantitative design rules for next-generation agrivoltaic materials that could improve both crop productivity and solar energy yields across diverse climates worldwide.

\vspace{1em}

%=============================================================================
% KEYWORDS
%=============================================================================

\noindent\textbf{Keywords:} Agrivoltaics, Quantum photosynthesis, Spectral engineering, Non-Markovian dynamics, Renewable energy, Organic photovoltaics, Coherence-assisted transport, Sustainable agriculture

%=============================================================================
% MAIN CONTENT (MODULAR SECTIONS)
%=============================================================================

\input{files2/introduction}

\input{files2/theory_methods}

\input{files2/results}

\input{files2/discussion}

\input{files2/conclusion}

%=============================================================================
% ACKNOWLEDGMENTS
%=============================================================================

\section*{Acknowledgments}

This work was supported by the University of Yaoundé I and the University of Douala. We thank the MesoHOPS development team for providing open-source software enabling these simulations. 

%=============================================================================
% DATA AVAILABILITY
%=============================================================================

\section*{Data availability statement}

All data supporting the findings of this study are available within the article and its Supporting Information. Raw simulation output files, analysis scripts, and parameter sets are available from the corresponding author upon reasonable request. The MesoHOPS simulation package used in this work is freely available at \url{https://github.com/MesoscienceLab/mesohops}.

%=============================================================================
% CONFLICTS OF INTEREST
%=============================================================================

\section*{Conflicts of Interest}

The authors declare no conflicts of interest.

%=============================================================================
% AUTHOR CONTRIBUTIONS
%=============================================================================

\section*{Author Contributions}

\textbf{Steve Cabrel Teguia Kouam}: Methodology, Validation, Formal analysis, Writing -- original draft. \textbf{Theodore Goumai Vodekoi}: Software, Investigation, Data curation, Writing -- original draft. \textbf{Jean-Pierre Tchapet Njafa}: Conceptualization, Theoretical framework, Writing -- review \& editing. \textbf{Jean-Pierre Nguenang}: Resources, Supervision, Formal analysis. \textbf{Serge Guy Nana Engo}: Project administration, Funding acquisition, final Manuscript editing. All authors have given approval to the final version of the manuscript.

%=============================================================================
% REFERENCES
%=============================================================================

\bibliographystyle{unsrt}  % Numbered references per RSC style
\bibliography{references}  % BibTeX file with all references

%=============================================================================
% SUPPORTING INFORMATION
%=============================================================================

\section*{Supporting Information}

Supporting Information includes detailed environmental factor models, biodegradability assessment, extended validation data (12 tests), complete FMO parameter sets, computational performance benchmarks, and supplementary figures S1--S7.

%=============================================================================
\end{document}
%=============================================================================
